A Massive Molecular Gas Reservoir in the $z$\,=\,2.221 Type-2 Quasar Host Galaxy SMM\,J0939+8315 lensed by the Radio Galaxy 3C220.3

### 2016-01-13 mod1/response.md

> We added notes in the caption of Table 4 to recap all assumptions
  used in deriving these quantities, as suggested.

6:
- Section 5: why do the authors cherry-pick these 2 SMGs to make
  comparisons? there are many other sources that could be chosen with
  a range of properties. A comparison to these 2 SMGs is not useful at
  all given the diversity in this population (e.g. the sentence "This
  demonstrates the large ..." is not true when comparing only 3
  objects). I suggest comparing to the general properties observed for
  SMGs (as summarized in CW14 or Casey+14) which will be more useful
  in placing this object in the context of the SMG population.

> We took into account this comment by adding a compilation of SMG and
  type-2 QSOs properties to Table 4. Please see the table notes and
  comments for details. We have therefore included a comparison to
  these sample-averaged values in our conclusion.  We initially picked
  out two well-studied and apparently similarly bright (submillimeter
  fluxes >400 mJy) gravitationally lensed SMGs, to be able to
  investigate a broader range of physical properties - some of which
  are not as well-constrained for the broader population. Thus, we
  decided to also keep this comparison in the paper.

7.
- the discussion/conclusions should focus on what is new from this
  paper and not what is already presented in H14. E.g. the last
  sentence about this SMG transitioning from starburst to QSO
  phase. How is that conclusion made or strengthened with this new
  data?

@@

2:
- section headings in 3 are strange. Remove the words "New results"
  since this is obvious and a requirement for publication. Also remove
  subheading or second line in heading 3.2.

> We removed "New results" in the subject headings, as suggested.

3:
- the left panels on Fig 1 and 2 should show the same region (have the
  same RA/DEC axes). It is also tough to tell by eye if the VLA9GHz
  and SMA emission is coincident. Perhaps these can be overlaid on
  Fig 1.

> We adjusted the panel sizes as suggested, and marked the locations
  of the peak emission from the SMA as blue crosses on the right
  panel in Figure 1.

### 2016-01-13 mod1/manuscript/ms.tex
strip off comments before resubmission

\slugcomment{Submitted to the ApJ}
\input{changelog.tex}       % git revision hash, new command

@@

\begin{document}
{\tiny  \RevisionInfo}        % place it here
\title{A Massive Molecular Gas Reservoir in the $z$\,=\,2.221 Type-2 Quasar Host Galaxy SMM\,J0939+8315 lensed by the Radio Galaxy 3C220.3}
\author{T. K. Daisy Leung and Dominik A. Riechers}
\affil{Department of Astronomy, Space Sciences Building, Cornell University, Ithaca, NY 14853, USA; \myemail}

@@

\section{Introduction}\label{sec:intro}
{\bf Submillimeter-selected galaxies (SMGs) are predominantly found at redshifts $z$\,$\sim$\,1\,--\,3 \citep{Chapman05a}, during the epoch of stellar mass and
galaxy assembly, with a tail out to $z>$ 6 \citep{Riechers13a}. 
%This galaxy population was first detected 
%$\sim$18 years ago with the Submillimeter Common User Bolometer Array (SCUBA) on the James
%Clerk Maxwell Telescope (JCMT; \citealt{Smail97a, Hughes98a, Barger98a}). 
Previous works %following this discovery
have shown that SMGs
 are extremely luminous in the infrared
 wavelengths (L$_\textrm{IR} \sim$ 10$^{12}$ \Lsun) with high star formation rates \citep[SFR $\gtrsim$\,500\,\Msun yr\pmOne; see \eg reviews by][]{Blain02a, Lagache05a,Casey14a}.  
{\bf Following the pioneering works in the discovery of this population \citep{Smail97a,Hughes98a,Barger98a}}, considerable amounts of effort have been invested into 
obtaining large samples of SMGs by carrying out
  large sky surveys with (sub)-mm facilities such as the {\it Herschel Space Observatory} \citep[\eg H-ATLAS, SPT, HerMES; ][]{Eales10a,Carlstrom11a,Oliver12a}.  
  }

  To characterize the physical properties of the gas reservoirs in the interstellar medium (ISM) where active star formation takes place, carbon monoxide ($^{12}$CO) rotational lines have been commonly used as tracers due to its high abundance in the ISM as well as its low excitation energy; the ground state transition line thereby directly probes the cool gas that is essential to fuel star formation \citep[see \eg reviews by][]{Solomon05a,Carilli13a}.{ \bf Observations of CO in SMGs 
  %at $z$\,$\sim$\,1\,--\,3 
  have demonstrated that these galaxies have large gas reservoirs typical of \textgreater 10$^{10}$\Msun \citep[\eg][]{Frayer98a, Neri03a, Riechers11c, Riechers11d, Ivison11a, Bothwell13a}.}

@@

\section{Analysis}
\subsection{Lens Modelling} \label{sec:Lens}
To study the intrinsic properties of the background galaxy, we determine the magnification factor {\bf and the half-light radius of the dust region} by performing
lens modeling on the SMA 1\,mm continuum data presented by H14 of this system. 
Lens modeling is carried out in the visibility
({\it uv-}) plane using an updated version of the publicly available software {\sc uvmcmcfit} \citep{uvmcmcfit15a},
details of the parametric lens model can be found in \citet{Bussmann15a}. 
{\bf The surface mass densities of the two lensing galaxies, 3C220.3 and its companion galaxy B, are described by singular isothermal ellipsoid profiles, and the source is assumed to have an
elliptical Gaussian profile. }

%We fix the phase center to coordinates ($\alpha$,\,$\delta$)\,\,(J2000) = (9$^{\rm h}$39$^{\rm m}$23\fs54,\,\,83\degr15\arcmin26\farcs10), where the
%angular offsets of the lenses and source are referenced to this position. The primary lens (3C220.3) is
%described by five free parameters: the angular offset ($\Delta \alpha_{\rm
%lens0}$ and $\Delta \delta_\textrm{lens0}$) relative to
%the chosen phase center ($\alpha$,\,$\delta$) in the image, the angular Einstein radius ($\theta_\textrm{E0}$), the
%axial ratio ($q_\textrm{lens0}$), and the position angle ($\phi_\textrm{lens0}$). The secondary lens (companion B) is
%described by three free parameters: $\theta_\textrm{E1}$, $q_\textrm{lens1}$, and $\phi_\textrm{lens1}$. The angular offset
%of the secondary
%lens is sampled with respect to that of
%the primary lens ($\Delta \alpha_\textrm{lens0}$ and $\Delta \delta_\textrm{lens0}$); we therefore do not consider ($\Delta \alpha_\textrm{lens1}$ and $\Delta \delta_\textrm{lens1}$)  as free parameters.
%The source (SMM\,J0939) is parameterized by
%six parameters: the position of the source relative to the
%primary lens ($\Delta \alpha_\textrm{s}$ and $\Delta
%\delta_\textrm{s}$), the total intrinsic flux density ($S_\nu$), the
%effective radius ($r_\textrm{s}\,=\,\sqrt{a_\textrm{s} b_\textrm{s}}$), the axial
%ratio ($q_\textrm{s}$\,=\, $b_\textrm{s}/a_\textrm{s}$), and the position angle
%($\phi_\textrm{s}$).The axial ratios of the lenses are restricted to $q_\textrm{lens} > 0.3$. 
%The best-fit model is obtained by maximizing the
%Gaussian likelihood function $ \mathcal{L} $ of the interferometric data in the Fourier domain.
%We initialize 512
%walkers and 6000 steps to identify the best-fit model parameters.

%We initialize the positions and Einstein radii of both lenses, and the position of the source using those
 %from the best-fit lens model performed on Keck K-band (near-infrared) data (H14). For each of
%these parameters, we impose a uniform prior in the range $\in\pm$3$\sigma$, where $\sigma$ is the uncertainty
%reported in their paper. 
\begin{figure}[!tbpH]
\centering
\includegraphics[width=0.232\textwidth]{f4.eps}
\includegraphics[width=0.232\textwidth]{f5.eps}
\caption{Double-lens modeling of SMM\,J0939 using {\sc uvmcmcfit} on the SMA 1\,mm continuum data.
The contours start at $\pm$2$\sigma$, incrementing at
steps of $\pm$2$\sqrt{\rm 2}\sigma$ in both panels. Left: SMA 1\,mm continuum (red contours) overlaid on the best-fit model (grayscale image), assuming an elliptical Gaussian profile for the background SMG. The lenses are represented by the black dots, the half-light area of the background source is represented by the magenta ellipse, {\bf and the critical curves are represented by the green ellipses.}
Right: Residual contours and image obtained by taking the Fourier transform of the difference between the SMA data and the best-fit model in the visibility plane. Solid (dashed) contours show the positive (negative) residuals.\label{fig:lens}}
\end{figure}

@@

{\bf Since SMM\,J0939 also hosts a type-2 quasar, we compare its properties}
against those of eight CO-detected obscured AGNs at $z$ = 1.6\,$-$\,2.8 \citep[][and references
therein]{Polletta11a}. 
Among these obscured quasars, F10214 has the lowest molecular gas mass as well as SFR. The fact that the gas mass of F10214 in their compilation was derived using \CO line emission \citep{Solomon05a} has a minor effect on the resulting low gas mass; \citet{Riechers11a} report
a similarly low gas mass derived using their CO($J$\,=\,1\,\rarr\,0) line emission.
With F10214 being the most strongly-lensed high-redshift type-2 quasar \citep[$\mu_{\textrm L}$ = 17; ][]{Solomon05a}\footnote{Note that \citet{Deane13a} suggest a magnification factor of $\mu_{\textrm L}$ = 6\,$\pm$\,1.5 for the CO emission in F10214.}, its exceptionally low molecular gas mass and SFR is evident that this source lies on the low end of the CO and IR luminosity distributions of the population.
In contrast to what was found for F10214, we find that the properties
(\eg FWHM of the CO line profile 
%\footnote{The statistical mean is based on the line profile of the CO transition closest to $J$ = 4\,\rarr\,3 available for each source.}
, M$_\textrm{gas}$
%\footnote{The molecular gas mass for each source is derived based on its lowest-$J$ CO line emission available in literature.}
, and SFE) of SMM\,J0939 are similar to the statistical means, except for the SFR, which is lower by a
factor of $\sim$\,1.5, but is nevertheless consistent within the measurement uncertainties. {\bf We thus find that the gas mass in SMM\,J0939 is consistent with other type-2 quasars. }

@@

% --> its short phase in the proposed evolutionary link  
%fits in the proposed evolutionary paradigm \citep[\eg][]{Sanders88,Coppin08a,Simpson12a}, in which it

>>>>

\slugcomment{Submitted to the ApJ}
%\input{changelog.tex}

@@

\begin{document}
%{\tiny  \RevisionInfo}
\title{A Massive Molecular Gas Reservoir in the $z$\,=\,2.221 Type-2 Quasar Host Galaxy SMM\,J0939+8315 lensed by the Radio Galaxy 3C220.3}
\author{T. K. Daisy Leung and Dominik A. Riechers}
\affil{Department of Astronomy, Space Sciences Building, Cornell University, Ithaca, NY 14853, USA; \myemail}

@@

\section{Introduction}\label{sec:intro}
{\bf Submillimeter-selected galaxies (SMGs) are predominantly found at redshifts $z$\,$\sim$\,1\,--\,3 \citep{Chapman05a}, during the epoch of stellar mass and
galaxy assembly, with a tail out to $z>$ 6 \citep{Riechers13a}.
Previous works
have shown that SMGs
 are extremely luminous in the infrared
 wavelengths (L$_\textrm{IR} \sim$ 10$^{12}$ \Lsun) with high star formation rates \citep[SFR $\gtrsim$\,500\,\Msun yr\pmOne; see \eg reviews by][]{Blain02a, Lagache05a,Casey14a}.
{\bf Following the pioneering works in the discovery of this population \citep{Smail97a,Hughes98a,Barger98a}}, considerable amounts of effort have been invested into
obtaining large samples of SMGs by carrying out
  large sky surveys with (sub)-mm facilities such as the {\it Herschel Space Observatory} \citep[\eg H-ATLAS, SPT, HerMES; ][]{Eales10a,Carlstrom11a,Oliver12a}.
  }

  To characterize the physical properties of the gas reservoirs in the interstellar medium (ISM) where active star formation takes place, carbon monoxide ($^{12}$CO) rotational lines have been commonly used as tracers due to its high abundance in the ISM as well as its low excitation energy; the ground state transition line thereby directly probes the cool gas that is essential to fuel star formation \citep[see \eg reviews by][]{Solomon05a,Carilli13a}.{ \bf Observations of CO in SMGs
  have demonstrated that these galaxies have large gas reservoirs typical of \textgreater 10$^{10}$\Msun \citep[\eg][]{Frayer98a, Neri03a, Riechers11c, Riechers11d, Ivison11a, Bothwell13a}.}

@@

\section{Analysis}
\subsection{Lens Modelling} \label{sec:Lens}
To study the intrinsic properties of the background galaxy, we determine the magnification factor {\bf and the half-light radius of the dust region} by performing
lens modeling on the SMA 1\,mm continuum data presented by H14 of this system.
Lens modeling is carried out in the visibility
({\it uv-}) plane using an updated version of the publicly available software {\sc uvmcmcfit} \citep{uvmcmcfit15a},
details of the parametric lens model can be found in \citet{Bussmann15a}.
{\bf The surface mass densities of the two lensing galaxies, 3C220.3 and its companion galaxy B, are described by singular isothermal ellipsoid profiles, and the source is assumed to have an
elliptical Gaussian profile. }
\begin{figure}[!tbpH]
\centering
\includegraphics[width=0.232\textwidth]{f4.eps}
\includegraphics[width=0.232\textwidth]{f5.eps}
\caption{Double-lens modeling of SMM\,J0939 using {\sc uvmcmcfit} on the SMA 1\,mm continuum data.
The contours start at $\pm$2$\sigma$, incrementing at
steps of $\pm$2$\sqrt{\rm 2}\sigma$ in both panels. Left: SMA 1\,mm continuum (red contours) overlaid on the best-fit model (grayscale image), assuming an elliptical Gaussian profile for the background SMG. The lenses are represented by the black dots, the half-light area of the background source is represented by the magenta ellipse, {\bf and the critical curves are represented by the green ellipses.}
Right: Residual contours and image obtained by taking the Fourier transform of the difference between the SMA data and the best-fit model in the visibility plane. Solid (dashed) contours show the positive (negative) residuals.\label{fig:lens}}
\end{figure}

@@

{\bf Since SMM\,J0939 also hosts a type-2 quasar, we compare its properties}
against those of eight CO-detected obscured AGNs at $z$ = 1.6\,$-$\,2.8 \citep[][and references
therein]{Polletta11a}.
Among these obscured quasars, F10214 has the lowest molecular gas mass as well as SFR. The fact that the gas mass of F10214 in their compilation was derived using \CO line emission \citep{Solomon05a} has a minor effect on the resulting low gas mass; \citet{Riechers11a} report
a similarly low gas mass derived using their CO($J$\,=\,1\,\rarr\,0) line emission.
With F10214 being the most strongly-lensed high-redshift type-2 quasar \citep[$\mu_{\textrm L}$ = 17; ][]{Solomon05a}\footnote{Note that \citet{Deane13a} suggest a magnification factor of $\mu_{\textrm L}$ = 6\,$\pm$\,1.5 for the CO emission in F10214.}, its exceptionally low molecular gas mass and SFR is evident that this source lies on the low end of the CO and IR luminosity distributions of the population.
In contrast to what was found for F10214, we find that the properties
(\eg FWHM of the CO line profile, M$_\textrm{gas}$, and SFE) of SMM\,J0939 are similar to the statistical means, except for the SFR, which is lower by a
factor of $\sim$\,1.5, but is nevertheless consistent within the measurement uncertainties. {\bf We thus find that the gas mass in SMM\,J0939 is consistent with other type-2 quasars. }

@@
